Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
squeeze paragraph

\item The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'{>}k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$. This is done according to the following argument, depicted in Fig \ref{fig:ct}.

A stable control system is known to have converging dynamics. 
Assume the closed-loop matrix eigenvalues are not repeated (which is sensible to do, since we select them). 
The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues;  
however, this in general not the case when dealing with complex eigenvalues.  
Consider the closed-loop matrix, which updates the states every discrete time step, 
and select the eigenvalue with smallest (non trivial) imaginary value -- call such value $\vartheta$. 
At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
surely after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
This $k$ is then taken to be the completeness threshold.

>>>>

\item The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that boundaries are not
violated for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$. This is done according to the following argument, 
shown in Fig~\ref{fig:ct}.

A stable control system is known to have converging dynamics. 
Assume the closed-loop matrix eigenvalues are not repeated 
(which is sensible to do, since we select them). 
The trajectories distance from the reference point (in this case the origin) 
decreases over time within subspaces related to real-valued eigenvalues;  
however, this in general not the case when dealing with complex eigenvalues.  
Consider the closed-loop matrix, which updates the states every discrete time step, 
and select the eigenvalue with smallest (non-trivial) imaginary value -- call such value $\vartheta$. 
At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
This $k$ is taken to be the completeness threshold.
